How Significant was WW2 in the Development of the Computer?

### 2017-02-02 Draft 2/Section 2 - Turing Machines.tex
Added remaining boolean conditions, and conditional function

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
    \hhline{====}
    $\mathbb{\mathbf{b}def}$(\textit{p},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{n}$($\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C}),\textfrak{E}) \\
    $\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C})   & - & P0, R, P\textit{p}, L & \textfrak{C} \\
    \hhline{====}
    $\mathbb{\mathbf{b}copy}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E}),\textfrak{E},\textit{r}) \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                       & other, none & - & \textfrak{E} \\
\end{tabu}

@@

The first takes one pointer \textit{p}, finds the first free bit (\textit{p}-square) on the tape, writes the dummy value of \texttt{0} to it and marks it with \textit{p}. This method of appendng makes the assumption that no \textit{p}-squares are left empty across the used tape - in order to preserve this, we shall only append to \textit{p}-squares directly at the end of the used tape, and we shall never erase \textit{p}-squares. The second very simply finds the bit at pointer \textit{r}, and branches to write either \texttt{0} or \texttt{1} at the bit at the pointer \textit{w}

Next, similar to as we did in $\lambda$-calculus, we shall define boolean operations. Every operation will take one or many pointers as arguments, and write the evaluated result to another given pointer. The simplest of these we can create is the negator:

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    $\mathbb{\mathbf{b}neg}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                       & other, none & - & \textfrak{E} \\
\end{tabu}

@@

This is almost identical to the copying function, but inverting the written symbols.56

>>>>

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
    \hhline{====}
    $\mathbb{\mathbf{b}def}$(\textit{p},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{n}$($\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C}),\textfrak{E}) \\
    $\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C})   & - & P0, R, P\textit{p}, L & \textfrak{C} \\
    \hhline{====}
    $\mathbb{\mathbf{b}copy}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E}),\textfrak{E},\textit{r}) \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                       & other & - & \textfrak{E} \\
\end{tabu}

@@

The first takes one pointer \textit{p}, finds the first free bit (\textit{p}-square) on the tape, writes the dummy value of \texttt{0} to it and marks it with \textit{p}. This method of appendng makes the assumption that no \textit{p}-squares are left empty across the used tape - in order to preserve this, we shall only append to \textit{p}-squares directly at the end of the used tape, and we shall never erase \textit{p}-squares. The second very simply finds the bit at pointer \textit{r}, and branches to write either \texttt{0} or \texttt{1} at the bit at the pointer \textit{w}.

\subsubsection{Boolean Operations}

As we did in $\lambda$-calculus, we shall define boolean operations. Every operation will take one or many pointers as arguments, and write the evaluated result to another given pointer. The simplest of these we can create is the negator:

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    $\mathbb{\mathbf{b}neg}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                       & other & - & \textfrak{E} \\
\end{tabu}

\medskip
This is almost identical to the copying function, but inverting the written symbols. The definition of the remaining logical functions based on truth tables now becomes simple:

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    $\mathbb{\mathbf{b}and}$(\textit{a},\textit{b},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C}),\textfrak{E}) \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
                                                                                       & 1 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
                                                                                       & other & - & \textfrak{E} \\
    \hhline{====}
    $\mathbb{\mathbf{b}or}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}or}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{\mathbf{b}or}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
                                                                                       & 0 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                       & other & - & \textfrak{E} \\
    \hhline{====}
    $\mathbb{\mathbf{b}xor}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}xor}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
    \hhline{----}
    \multirow{3}{*}{$\mathbb{\mathbf{b}xor}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
                                                                                       & 0 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
                                                                                       & 1 & - &  $\mathbb{\mathbf{b}not}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
                                                                                       & other & - & \textfrak{E} \\
\end{tabu}

\medskip
In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-calculus. Gradually, the cryptic and simplified language of Finite State Machines is yielding results similar to that of a computer.

\subsubsection{Simplified Configurations}

As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions. We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.

\medskip\noindent\begin{tabu} to \textwidth{XXXX}
    \multirow{2}{*}{$\mathbb{if}$(\textit{c},\textfrak{I},\textfrak{O})} 
                                                                                       & \textit{c} & - & \textfrak{I} \\
                                                                                       & other & - & \textfrak{O} \\ 
    \hhline{====}
    $\mathbb{ifp}$(\textit{r},\textit{c},\textfrak{I},\textfrak{O}, \textfrak{E}) & - & - & $\mathbb{fl}$($\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O}), \textfrak{E}, \textit{r}) \\
\end{tabu}

@@

Since we have now entirely defined the operation of the machine in terms of functions, we no longer have any need for tables.
